INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION

### 2016-09-13 paper.tex
Fix title
Do not use second bibtex file
Update abstract

% Title.
% ------
\title{INVARIANT REPRESENTATIONS FOR SPEECH RECOGNITION}
%
% Single address.
% ---------------
%\name{Dmitriy Serdyuk $^{\dagger}$ \qquad Kartik Audhkhasi$^{\star}$ \and Philemon Brakel$^{\dagger}$ \and Bhuvana Ramabhadran$^{\star}$  \and Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
%\address{$^{\dagger}$ Universit\'e de Montr\'eal, $^{\star}$ IBM}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
\twoauthors
  {Dmitriy Serdyuk $^{\dagger}$\thanks{Dmitriy Serdyuk performed the work
  while at IBM}, Kartik Audhkhasi$^{\star}$, Philemon Brakel$^{\dagger}$, Bhuvana Ramabhadran$^{\star}$, Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
  {$^{\dagger}$ Universit\'e de Montr\'eal \\
  $^{\star}$ IBM}
  {}
  {}

\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
    Robustness of a speech recognition system is a challenging task and modern
    automatic speech recognition (ASR) systems need to be robust to different recording conditions,
    microphone type, accents, and noisy recording environment. We mitigate
    this problem in a fashion similar to recent research on image generation using
    Generative Adversarial Networks and domain adaptation ideas extending
    adversarial gradient-based training.
    This work focuses on investigation of neural architectures which produce
    representations invariant to certain conditions as gender and noise type. We
    experimentally evaluate proposed architectures on the acoustic modelling task
    for speech recognition on the Aurora4 dataset.
\end{abstract}
%
\begin{keywords}
speech recognition, deep neural networks, invariant representations, adversarial training
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

@@

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEE}
\bibliography{strings,refs}

>>>>

% Title.
% ------
\title{INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION}
%
% Single address.
% ---------------
%\name{Dmitriy Serdyuk $^{\dagger}$ \qquad Kartik Audhkhasi$^{\star}$ \and Philemon Brakel$^{\dagger}$ \and Bhuvana Ramabhadran$^{\star}$  \and Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
%\address{$^{\dagger}$ Universit\'e de Montr\'eal, $^{\star}$ IBM}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
\twoauthors
  {Dmitriy Serdyuk $^{\dagger}$\thanks{Dmitriy Serdyuk performed the work
  while at IBM}, Kartik Audhkhasi$^{\star}$, Philemon Brakel$^{\dagger}$, Bhuvana Ramabhadran$^{\star}$, Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
  {$^{\dagger}$ Universit\'e de Montr\'eal \\
  $^{\star}$ IBM}
  {}
  {}

\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
    Robustness of a speech recognition system is a challenging task and modern
    automatic speech recognition (ASR) systems need to be resilient to different recording conditions,
    microphone type, accents, and noisy recording environment. We mitigate
    this problem in a fashion similar to recent research on image generation using
    Generative Adversarial Networks and domain adaptation ideas extending
    adversarial gradient-based training. A recent work of Ganin et al. proposes to
    use adversarial training procedure for image domain adaptation making an intermediate
    representation to improve the target performance and at the same time
    to deteriorate the domain classifier performance, which is a separate neural
    network taking the intermediate representation as the input.

    This work focuses on investigation of neural architectures which produce
    representations invariant to certain conditions as the noise type for speech
    recognition. Similar
    to the Ganin et al. work we train the intermediate representation to be invariant
    to noise conditions training three neural networks: the encoder, the recognizer, and the
    noise classifier to produce the representation produced by the encoder to decrease
    the performance of the classifier making the representation invariant to noise conditions. We
    experimentally evaluate proposed architectures on the acoustic modelling task
    for speech recognition on a popular benchmark Aurora4.
\end{abstract}
%
\begin{keywords}
speech recognition, deep neural networks, invariant representations, adversarial training
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

@@

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEE}
\bibliography{refs}
